\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
<!--radix_placeholder_navigation_in_header-->
<meta name="distill:offset" content=""/>

<script type="application/javascript">

  window.headroom_prevent_pin = false;

  window.document.addEventListener("DOMContentLoaded", function (event) {

    // initialize headroom for banner
    var header = $('header').get(0);
    var headerHeight = header.offsetHeight;
    var headroom = new Headroom(header, {
      tolerance: 5,
      onPin : function() {
        if (window.headroom_prevent_pin) {
          window.headroom_prevent_pin = false;
          headroom.unpin();
        }
      }
    });
    headroom.init();
    if(window.location.hash)
      headroom.unpin();
    $(header).addClass('headroom--transition');

    // offset scroll location for banner on hash change
    // (see: https://github.com/WickyNilliams/headroom.js/issues/38)
    window.addEventListener("hashchange", function(event) {
      window.scrollTo(0, window.pageYOffset - (headerHeight + 25));
    });

    // responsive menu
    $('.distill-site-header').each(function(i, val) {
      var topnav = $(this);
      var toggle = topnav.find('.nav-toggle');
      toggle.on('click', function() {
        topnav.toggleClass('responsive');
      });
    });

    // nav dropdowns
    $('.nav-dropbtn').click(function(e) {
      $(this).next('.nav-dropdown-content').toggleClass('nav-dropdown-active');
      $(this).parent().siblings('.nav-dropdown')
         .children('.nav-dropdown-content').removeClass('nav-dropdown-active');
    });
    $("body").click(function(e){
      $('.nav-dropdown-content').removeClass('nav-dropdown-active');
    });
    $(".nav-dropdown").click(function(e){
      e.stopPropagation();
    });
  });
</script>

<style type="text/css">

/* Theme (user-documented overrideables for nav appearance) */

.distill-site-nav {
  color: rgba(255, 255, 255, 0.8);
  background-color: #0F2E3D;
  font-size: 15px;
  font-weight: 300;
}

.distill-site-nav a {
  color: inherit;
  text-decoration: none;
}

.distill-site-nav a:hover {
  color: white;
}

@media print {
  .distill-site-nav {
    display: none;
  }
}

.distill-site-header {

}

.distill-site-footer {

}


/* Site Header */

.distill-site-header {
  width: 100%;
  box-sizing: border-box;
  z-index: 3;
}

.distill-site-header .nav-left {
  display: inline-block;
  margin-left: 8px;
}

@media screen and (max-width: 768px) {
  .distill-site-header .nav-left {
    margin-left: 0;
  }
}


.distill-site-header .nav-right {
  float: right;
  margin-right: 8px;
}

.distill-site-header a,
.distill-site-header .title {
  display: inline-block;
  text-align: center;
  padding: 14px 10px 14px 10px;
}

.distill-site-header .title {
  font-size: 18px;
  min-width: 150px;
}

.distill-site-header .logo {
  padding: 0;
}

.distill-site-header .logo img {
  display: none;
  max-height: 20px;
  width: auto;
  margin-bottom: -4px;
}

.distill-site-header .nav-image img {
  max-height: 18px;
  width: auto;
  display: inline-block;
  margin-bottom: -3px;
}



@media screen and (min-width: 1000px) {
  .distill-site-header .logo img {
    display: inline-block;
  }
  .distill-site-header .nav-left {
    margin-left: 20px;
  }
  .distill-site-header .nav-right {
    margin-right: 20px;
  }
  .distill-site-header .title {
    padding-left: 12px;
  }
}


.distill-site-header .nav-toggle {
  display: none;
}

.nav-dropdown {
  display: inline-block;
  position: relative;
}

.nav-dropdown .nav-dropbtn {
  border: none;
  outline: none;
  color: rgba(255, 255, 255, 0.8);
  padding: 16px 10px;
  background-color: transparent;
  font-family: inherit;
  font-size: inherit;
  font-weight: inherit;
  margin: 0;
  margin-top: 1px;
  z-index: 2;
}

.nav-dropdown-content {
  display: none;
  position: absolute;
  background-color: white;
  min-width: 200px;
  border: 1px solid rgba(0,0,0,0.15);
  border-radius: 4px;
  box-shadow: 0px 8px 16px 0px rgba(0,0,0,0.1);
  z-index: 1;
  margin-top: 2px;
  white-space: nowrap;
  padding-top: 4px;
  padding-bottom: 4px;
}

.nav-dropdown-content hr {
  margin-top: 4px;
  margin-bottom: 4px;
  border: none;
  border-bottom: 1px solid rgba(0, 0, 0, 0.1);
}

.nav-dropdown-active {
  display: block;
}

.nav-dropdown-content a, .nav-dropdown-content .nav-dropdown-header {
  color: black;
  padding: 6px 24px;
  text-decoration: none;
  display: block;
  text-align: left;
}

.nav-dropdown-content .nav-dropdown-header {
  display: block;
  padding: 5px 24px;
  padding-bottom: 0;
  text-transform: uppercase;
  font-size: 14px;
  color: #999999;
  white-space: nowrap;
}

.nav-dropdown:hover .nav-dropbtn {
  color: white;
}

.nav-dropdown-content a:hover {
  background-color: #ddd;
  color: black;
}

.nav-right .nav-dropdown-content {
  margin-left: -45%;
  right: 0;
}

@media screen and (max-width: 768px) {
  .distill-site-header a, .distill-site-header .nav-dropdown  {display: none;}
  .distill-site-header a.nav-toggle {
    float: right;
    display: block;
  }
  .distill-site-header .title {
    margin-left: 0;
  }
  .distill-site-header .nav-right {
    margin-right: 0;
  }
  .distill-site-header {
    overflow: hidden;
  }
  .nav-right .nav-dropdown-content {
    margin-left: 0;
  }
}


@media screen and (max-width: 768px) {
  .distill-site-header.responsive {position: relative; min-height: 500px; }
  .distill-site-header.responsive a.nav-toggle {
    position: absolute;
    right: 0;
    top: 0;
  }
  .distill-site-header.responsive a,
  .distill-site-header.responsive .nav-dropdown {
    display: block;
    text-align: left;
  }
  .distill-site-header.responsive .nav-left,
  .distill-site-header.responsive .nav-right {
    width: 100%;
  }
  .distill-site-header.responsive .nav-dropdown {float: none;}
  .distill-site-header.responsive .nav-dropdown-content {position: relative;}
  .distill-site-header.responsive .nav-dropdown .nav-dropbtn {
    display: block;
    width: 100%;
    text-align: left;
  }
}

/* Site Footer */

.distill-site-footer {
  width: 100%;
  overflow: hidden;
  box-sizing: border-box;
  z-index: 3;
  margin-top: 30px;
  padding-top: 30px;
  padding-bottom: 30px;
  text-align: center;
}

/* Headroom */

d-title {
  padding-top: 6rem;
}

@media print {
  d-title {
    padding-top: 4rem;
  }
}

.headroom {
  z-index: 1000;
  position: fixed;
  top: 0;
  left: 0;
  right: 0;
}

.headroom--transition {
  transition: all .4s ease-in-out;
}

.headroom--unpinned {
  top: -100px;
}

.headroom--pinned {
  top: 0;
}

/* adjust viewport for navbar height */
/* helps vertically center bootstrap (non-distill) content */
.min-vh-100 {
  min-height: calc(100vh - 100px) !important;
}

</style>

<script src="site_libs/jquery-1.11.3/jquery.min.js"></script>
<link href="site_libs/font-awesome-5.1.0/css/all.css" rel="stylesheet"/>
<link href="site_libs/font-awesome-5.1.0/css/v4-shims.css" rel="stylesheet"/>
<script src="site_libs/headroom-0.9.4/headroom.min.js"></script>
<!--/radix_placeholder_navigation_in_header-->
<!--radix_placeholder_site_in_header-->
<!--/radix_placeholder_site_in_header-->

<style type="text/css">
body {
  padding-top: 60px;
}
</style>

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{\scriptsize  William Sealy Gosset - CV }
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={William Sealy Gosset:  CV (Curriculum Vitae)},
            pdfauthor={William Sealy Gosset},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf William Sealy Gosset}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Chief Brewer, Arthur Guinness \& Son}
\moveleft.5\hoffset\centerline{Guinness Brewery · Park Royal · London NW10 7RR, UK}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:guinness@consumer-care.net}{\nolinkurl{guinness@consumer-care.net}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  +353 1 408 4800  \hspace{1 mm}      \faGlobe \hspace{1 mm} \href{http://guinness.com}{\tt guinness.com}    | \emph{Updated:} \apstylekinda\today}

\vspace{2 mm}

\hrule


\hypertarget{employment}{%
\section{Employment}\label{employment}}

\emph{Arthur Guinness \& Son}

Chief Brewer (Park Royal) \hfill 1935-1937

Researcher (Dublin) \hfill 1899-1935

\hypertarget{education}{%
\section{Education}\label{education}}

\emph{New College, Oxford University}, B.A. Chemistry \hfill 1899

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{books}{%
\subsection{Books}\label{books}}

Pearson, E.S. and John Wishart (eds.). 1943. \emph{``Student's''
Collected Papers} London: Biometrika Office.

\hypertarget{journal-articles}{%
\subsection{Journal Articles}\label{journal-articles}}

Student. 1938. ``Comparison between Balanced and Random Arrangements on
Field Plots.'' \emph{Biometrika} 29(3-4): 363--378.

Student. 1936. ``Co-operation in Large Scale Experiments.''
\emph{Supplement to Journal of the Royal Statistical Society} 3(2):
115--136.

Student. 1931. ``On the \emph{z} Test.'' \emph{Biometrika} 23(3-4):
407-408.

Student. 1931. ``The Lanarkshire Milk Experiment.'' \emph{Biometrika}
23(3-4): 398--406.

Student. 1929. ``Statistics in Biological Research.'' \emph{Nature} 124:
93

Student. 1927. ``Errors of Routine Analysis.'' \emph{Biometrika}
19(1-2): 151--164.

Student. 1926. ``Mathematics and Agronomy.'' \emph{Journal of the
American Society of Agronomy} 18.

Student. 1925. ``New Tables for Testing the Significance of
Observations.'' \emph{Metron} 5(3): 105--108.

Student. 1923. ``On Testing Varieties of Cereals.'' \emph{Biometrika}
15(3-4): 271--293.

Student. 1921. ``An Experimental Determination of the Probable Error of
Dr.~Spearman's Correlation Co-efficient'' \emph{Biometrika} 13(2-3):
263--282.

Student. 1917. ``Tables for Estimating the Probability That the Given
Mean of a Unique Sample of Observations Lies between \(-\infty\) and Any
Given Distance of the Mean of the Population from Which the Sample Is
Drawn.'' \emph{Biometrika} 11(4): 414--417.

Student. 1909. ``The Distribution of the Means of Samples Which Are Not
Drawn at Random.'' \emph{Biometrika} 7(1-2): 210--214.

Student. 1908. ``Probable Error of a Correlation Coefficient.''
\emph{Biometrika} 6(2-3): 302--310.

Student. 1908. ``The Probable Error of a Mean.'' \emph{Biometrika} 6(1):
1--25.

Student. 1907. ``On the Error of Counting with a Haemacytometer.''
\emph{Biometrika} 5(3): 351--360.

\hypertarget{other-publications}{%
\subsection{Other Publications}\label{other-publications}}

Student. 1905. ``The Pearson Co-efficient of Correlation.'' Supplement
to Report of 1904, Arthur Guinness Son \& Company.

Student. 1904. ``The Application of the `Law of Error' to the Work of
the Brewery.'' Report, Arthur Guinness Son \& Company.

\hypertarget{references}{%
\section{References}\label{references}}

Available upon request, though likely would include Karl Pearson and
Ronald A. Fisher. Please send corrections, feedback, or details of
missed publications (of which there are probably a few) to
\href{mailto:svmille@clemson.edu}{\nolinkurl{svmille@clemson.edu}}.

<!--radix_placeholder_site_after_body-->
<!--/radix_placeholder_site_after_body-->

<!--radix_placeholder_navigation_after_body-->
<!--/radix_placeholder_navigation_after_body-->

\end{document}

